The Decline of Financial Wellness

### 2023-03-09 outputs/paper/paper3.qmd
updated data section - adding variable definitions

Specifically, we retrieved the following demographic data (TODO: explain these values)

-   cohort

-   degree

-   class

-   class1

-   sexbirth1

-   martial

-   realinc

-   income16

For survey questions related to financial wellness, we retrieved the following data points (TODO: explain these values):

-   confinan

-   satfin

-   finalter

-   finrela

@@

```{r}

{r}
#| message: false
#| echo: false
#| warning: false

>>>>

Specifically, we retrieved the following demographic data.

| Variable  | New Name | Description                    | Example              |
|-----------|----------|--------------------------------|----------------------|
| age       | age      | Respondent's age               | 56                   |
| cohort    | cohort   | Birth cohort of respondent     | 1965                 |
| sexbirth1 | gender   | sex recorded at birth          | Female               |
| marital   | marital  | Respondent's martial status    | Divorced             |
| degree    | degree   | Respondent's degree            | Bachelors            |
| income16  | income   | family income recorded in 2016 | \$50,000 TO \$59,999 |

For survey questions related to financial wellness, we retrieved the following data points:

| Variable | New Name               | Description                                                                             | Example               |
|---------|-----------------|----------------------------|------------------|
| satfin   | financial_satisfaction | Respondent's satisfaction with their current financial situation                        | Pretty Well Satisfied |
| finalter | financial_change       | Changes in respondent's financial situation                                             | Stayed the same       |
| finrela  | financial_compare      | Comparing respondent's family income with American families in general                  | Above Average         |
| class    | social_class           | self identified social class the respondent belong in                                   | Middle Class          |
| class1   | social_class1          | self identified social class the respondent belong in (more granular than social_class) | Upper Middle Class    |

@@
